\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-23 draft.tex
fix description of as:ga_ta, note in letter; closes #24

Assumption~\ref{as:ga_c} formalizes the intuition that the legislature favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity.\footnote{The diminishing returns here take the form of declining increments to the lobby's influence as effort increases; in Ethier (2012), the returns to lobbying decline as the level of protection increases.} It allows the political uncertainty inherent in $\ta$ to be correlated in interesting ways with the level of $e$, ruling out only (i) that higher effort levels make lower $\ga$-weights more likely and (ii) that effort and uncertainty are correlated in such a way that increasing lobbying effort changes the structure of uncertainty so that higher $\ga$-weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} formalizes the intuition that larger realization of the uncertainty variable $\ta$ increase the value of the political economy weight.

>>>>

Assumption~\ref{as:ga_c} formalizes the intuition that the legislature favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity.\footnote{The diminishing returns here take the form of declining increments to the lobby's influence as effort increases; in Ethier (2012), the returns to lobbying decline as the level of protection increases.} It allows the political uncertainty inherent in $\ta$ to be correlated in interesting ways with the level of $e$, ruling out only (i) that higher effort levels make lower $\ga$-weights more likely and (ii) that effort and uncertainty are correlated in such a way that increasing lobbying effort changes the structure of uncertainty so that higher $\ga$-weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} \textbf{simply provides for an intuitive labelling so that} larger realization of the uncertainty variable $\ta$ increase the value of the political economy weight.
